Variance reduction for MCMC methods via martingale representations

### 2020-02-18 aap/Revision/vr-mcmc-revision-new.tex
update vr-mcmc-revision-new.tex

and for all $x\in\mathbb R^d$, $j \in \{1,\dots,d\}$ and  \(\mathbf{k}\) satisfying \(0<\|\mathbf{k}\|\leq  K,\)

@@

|\partial_j^{\mathbf{k}} f(x)|\le  B_f, \quad |\partial_j^{\mathbf{k}} \mu (x)|\leq B_\mu \eqsp.

@@

For $l\le p$, we have the representation

@@

X_{p}=G_{p}(X_0,\sqrt{\gamma}Z_{1},\ldots,\sqrt{\gamma}Z_{p}),

@@

\eric{this notation is a bit confusing, $f \circ G_p$ is defined on $p (d+1)$ coordinates}

@@

\begin{lem}\label{eq:a_repr}
Fix some \(\mathbf{k},\mathbf{k}'\in \mathbb{N}_0^d\) with \(\mathbf{k}'\le \mathbf{k}\) componentswise.  Then the following representation holds
$$
\bar a_{p,\mathbf{k}}(x)=\left(\gamma^{|\mathbf{k}'|}\frac{(\mathbf{k}-\mathbf{k}') !}{\mathbf{k}!}\right)^{1/2}
\mathsf E\left[\left.
\partial_{1}^{\mathbf{k}'}f(X_p)\mathbf{H}_{\mathbf{k}-\mathbf{k}'}(Z_l)\right|X_{0}=x\right].
$$
\end{lem}

>>>>

and for all $x\in\mathbb R^d$ and  \(\mathbf{k}\) satisfying \(0<\|\mathbf{k}\|\leq  K,\)

@@

|\partial^{\mathbf{k}} f(x)|\le  B_f, \quad |\partial^{\mathbf{k}} \mu (x)|\leq B_\mu \eqsp.

@@

For $l\le p$ and $x \in \rset^d$, we have the representation

@@

X^x_{p}=G_{p}(x,\sqrt{\gamma}Z_{1},\ldots,\sqrt{\gamma}Z_{p}),

@@

@@

\begin{lem}\label{eq:a_repr}
Fix some \(\mathbf{k},\mathbf{k}'\in \mathbb{N}_0^d\) with \(\mathbf{k}'\le \mathbf{k}\) componentwise.  Then the following representation holds
\[
\bar a_{p,\mathbf{k}}(x)=\left(\gamma^{|\mathbf{k}'|}\frac{(\mathbf{k}-\mathbf{k}') !}{\mathbf{k}!}\right)^{1/2}
\PE\left[
\partial_{1}^{\mathbf{k}'}f(X^x_p)\mathbf{H}_{\mathbf{k}-\mathbf{k}'}(Z_l)\right] \eqsp.
\]
\end{lem}
